Single-fluorophore orientation determination with multiview polarized illumination: modeling and microscope design

### 2017-11-13 paper/paper/paper.tex
Patrick's edits to responses.

We thank the reviewer for this valuable comment. We neglected to comment on the
ability of our designs to image dipoles that are rotating during the measurement
time, so we have \hyperlink{temporal}{\color{urlblue} added a paragraph} to
address this omission. We highlight that the modeling in this work only applies
to fixed dipoles, so estimating the orientation of rotating dipoles using these
methods will, in general, lead to incorrect estimates. However, if the dipole
rotates through a small solid angle during the measurement time, the models used
in this paper will give a slightly biased estimate of the average orientation of
the dipole. The precision results in this paper for fixed dipoles apply to
rotating dipoles if the dipoles rotate through a small solid angle during the
measurement time. If the dipoles rotate through a large solid angle during the
measurement time, then further modeling is required to
accurately estimate the dipole orientation.\\

@@

\hypertarget{temporal}{{\color{urlblue} The models in this paper only consider
    estimating the orientation of fixed dipoles, but real dipoles change their
    orientation during measurement. Therefore, it is necessary to comment on the
    applicability of our results to dynamic dipoles. In general, using the
    models in this paper to estimate the orientation of rotating dipoles will
    lead to incorrect results. However, if a dipole rotates through a small
    solid angle during the measurement, the models in this paper will give a
    precise and slightly biased estimate of the average orientation of the
    dipole. The results in this paper apply to the precision of our estimates
    for the average dipole orientation of rotating dipoles, but the direction
    and size of the bias has not been characterized in detail. In future work we
    will model dynamic dipoles and attempt to estimate the average dipole
    orientation and the dipole's orientation distribution. Single-view polarized
    illumination techniques have already been used to study the orientation
    distribution of ensembles of dynamic dipoles \cite{mehta2016, backer2016},
    but multiview polarized illumination microscopes have not been investigated
    for this purpose.}}

>>>>

We thank the reviewer for this valuable comment. We neglected to comment on the
ability of our designs to image dipoles that are rotating during the measurement
time, so we have \hyperlink{temporal}{\color{urlblue} added a paragraph} to
address this omission. We highlight that the modeling in this work only applies
to fixed dipoles, so estimating the orientation of rotating dipoles using these
methods will, in general, lead to incorrect estimates. However, if the dipole
rotates through a small solid angle during the measurement time, the models used
in this paper will give a slightly biased estimate of the average orientation of
the dipole. If the dipoles rotate through a large solid angle during the
measurement time, then further modeling is required to
accurately estimate the dipole orientation.\\

@@

\hypertarget{temporal}{{\color{urlblue} The models in this paper only consider
    estimating the orientation of fixed dipoles, but real dipoles change their
    orientation during measurement. Therefore, it is necessary to comment on the
    applicability of our results to dynamic dipoles. In general, using the
    models in this paper to estimate the orientation of rotating dipoles will
    lead to incorrect results. However, if a dipole rotates through a small
    solid angle during the measurement, the models in this paper will give a
    slightly biased estimate of the average orientation of the dipole. The
    direction and size of the bias has not been characterized in detail. In
    future work we will model dynamic dipoles and attempt to estimate the
    average dipole orientation and the dipole's orientation
    distribution. Single-view polarized illumination techniques have already
    been used to study the orientation distribution of ensembles of dynamic
    dipoles \cite{mehta2016, backer2016}, but multiview polarized illumination
    microscopes have not been investigated for this purpose.}}
